R Notebook

### 2022-02-14 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd

                    #2nd passIt
passIt$substring_first <-     
  str_extract(
    passIt$X5,
    "(\\w+)")

@@

                      #3rd PassIt
passIt = subset(passIt, 
                       select = -c(3)
                       )
#####

@@

names(smugCovIdx )[1] <- "dnkName"
names(smugCovIdx )[2] <- "dnkIng"
names(smugCovIdx )[3] <- "dnkCode"   
names(smugCovIdx )[4] <- "classIng"

@@

# Network: Creating network Data

## Basic R: Brief Dataset Description
```{r Network: Identify critical features, echo=FALSE}
#### dimensions of an object
dim()

>>>>

colnames(passIt)
                    #2nd passIt
passIt$substring_first <- 
  str_extract(passIt$X5,"(\\w+)")

@@

                      #3rd PassIt
passIt = subset(passIt, 
                       select = -c(3)
                       )
colnames(passIt)
#####

@@

names(smugCovIdx )[1] <- "dnkName"
names(smugCovIdx )[2] <- "dnkIng"
names(smugCovIdx )[3] <- "ingType"

colnames(smugCovIdx)
```

# Network: Creating network Data
```{r EDGELIST: IGRAPH: create a network object from the dataset, echo=TRUE}

 dr_smugCov <- smugCovIdx

dr_smugCov <-
  graph.data.frame(smugCovIdx[,3:2,1],
                   directed = T)
summary(dr_smugCov)

plot(dr_smug_ntWrk)
plot(tst_ntwrk)
unDr_smug_ntWrk

@@

# Network Info
## Basic R: Brief Dataset Description
```{r Network: Identify critical features, echo=FALSE}
#### dimensions of an object
dim()
